Solution of Differential Algebraic Equations with Local Constraints on the Latent Space of an Autoencoder

### 2019-07-12 paper/paper.tex
new more citations

\begin{figure}
\centering
\includegraphics[width=4in]{../figures/water_eos.png}
\caption{\label{fig:pTrho} The $\log{p}$, $T$, $\rho$ equation of
  state surface for water in units of $\log{\text{Pa}}$, K, and \si{}{kg/m$^2$} This plot spans four phases, three
  equilibria, and the triple point, which are each given their own color.
  There is a fourth dimension to the surface of enthalpy $h$ that exhibits
  similar discontinuities; the $\log{p}$, $T$, $h$ surface is plotted
  in the Appendix. (Every point on this plot is a point in the
  generated dataset used for the optimization)}
\end{figure}

{\bf Remark:} There are even more known phases of crystal ice which for water
For water, the supercritical phase and exotic ices only occur in
laboratory conditions or naturally near the
crust \cite{}. For our case, we only handle the Ice I and cutoff the
regime at \si{10^8}{Pa}. For other materials these exotic phases can be
applicable. Methane $CH_4$ is actually well beyond its supercritical
point at T=\si{-82.59}{C}\cite{the_engineering_toolbox_methane_2008}, so only an appropriate gas law can do the trick, until
the bi-species hydrate phase comes into play.
The liquid-gas-equilibrium-supercritical state transition comes into
play in, for example, in geoengineered systems using $CO_2$
such as geothermal plants are carbon sequestration facilities, the
working fluid is often in the supercritical regime at depth, and the
phase boundary. cite
curt. cite hydrates.
When binary mixtures are involved, the number of possible phases and
equilibria increases again.

>>>>

\begin{figure}
\centering
\includegraphics[width=4in]{../figures/water_eos.png}
\caption{\label{fig:pTrho} The $\log{p}$, $T$, $\rho$ equation of
  state surface for water in units of $\log{\text{Pa}}$, K, and \si{}{kg/m$^2$} This plot spans four phases, three
  equilibria, and the triple point, which are each given their own color.
  There is a fourth dimension to the surface of enthalpy $h$ that exhibits
  similar discontinuities; the $\log{p}$, $T$, $h$ surface is plotted
  in the Appendix. (Every point on this plot is a point in the
  generated dataset used for the optimization.) An interactive version
of this figure is included online.}
\end{figure}

{\bf Remark:} There are even more known phases of crystal ice which for water
For water, the supercritical phase only occurs at extreme conditions
near the mantel or near magma chambers, which could be potential sites
for geothermal plants\cite{elders_science_2010}. The exotic ices only occur in
laboratory conditions\cite{water_revised_2009}. For our case, we only handle the Ice I and cutoff the
regime at \si{10^8}{Pa}. For other materials these exotic phases can be
applicable. Methane $CH_4$ is actually well beyond its supercritical
point at T=\si{-82.59}{C}\cite{the_engineering_toolbox_methane_2008}, so only an appropriate gas law can do the trick, until
the bi-species hydrate phase comes into play. Handling the
liquid-gas-equilibrium-supercritical state transition also comes into
play with other fluids; for example, in geoengineered systems using
$CO_2$ such as geothermal plants and carbon sequestration facilities, the
working fluid is often in the supercritical regime at depth, and the
phase boundary \cite{pruess_feasibility_2006,oldenburg_migration_2006}. 
When binary mixtures are involved, the number of possible phases and
equilibria increases again; methane hydrate simulators have 15
states \cite{moridis_simulation_2019}.
